Topic and tone of political news articles in German online media.

### 2018-05-08 paper/R/04_Modelresults_50.Rmd
paper submission

```{r include=FALSE}
library(ggplot2)     # Static data visualization
library(dplyr)       # Data manipulation
library(stringr)     # String manipulation
library(lubridate)   # Date and time manipulation
library(purrr)       # Functional programming
library(tidyr)       # Reshaping
library(magrittr)    # Advanced piping
library(pushoverr)   # Pushover notifications
library(readr)       # Importing data
library(data.table)
library(stm)
library(readxl)
library(Matrix)
library(psych)
library(xtable)
library(quanteda)

library(ggridges)
library(igraph)
library(corrplot)
#library(patchwork)
library(ggpmisc)
#library(ggraph)
library(ggiraph)
library(tidygraph)
library(RColorBrewer) 
library(ggrepel)
library(scales)      # Scales

@@

theme_set(
  theme_bw(base_family = "Roboto", base_size = 10) +
    theme(
      plot.title = element_text(size = 14,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 8),
      plot.caption = element_text(size = 6),
      panel.border = element_blank()
    )
)

rm(list=ls())
col <- rcartocolor::carto_pal(12, "Bold")
source("func/functions.R")
```

@@

```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col[8], alpha = 0.8) +
  labs(x="", y="Number of articles") +
  theme(
    axis.text.x = element_text(size = 9),
      legend.position   = "none"
    )

},
filename = "../figs/bar.png", device = "png", 
width = 7, height = 4,
        dpi = 600)
```

![plot1](../figs/bar.png)
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  group_by(date) %>%
  dplyr::summarise(obs = n()) %>%
  ggplot(aes(date, obs)) +
  geom_line(color=col[3]) +
  geom_vline(aes(xintercept=as.Date("2017-09-24")),
             linetype = 2, color=col[5]) +
  geom_vline(aes(xintercept=as.Date("2017-11-19")),
             linetype = 2, color=col[5]) +
  scale_color_manual(values = col) +
  labs(x="", y="Number of Articles",color="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(
      legend.position   = "none",
      axis.title.x      = element_blank(),
      axis.text       = element_text(size = 8)
    )
},
filename = "../figs/timeline.png", device = "png",width = 6, height = 4,
dpi = 600
)

@@

print(xtable(output, type="latex"), file="../writing/tables/wordcount.tex" )

@@

ggsave(plot = {
  btw %>%
    ggplot(aes(as.numeric(text_length.cut), site)) +
    geom_density_ridges(scale = 4,
                        fill = col[3], alpha = .8,
                        color = "white") +
    theme_ridges() +
    labs(x = "Word count", y = "") +
    scale_x_continuous(expand = c(0,0), 
                       labels = c(seq(0,1500,500), ">2000"))

@@

### Unprocessed Text
```{r message=FALSE, warning=FALSE}
all.corpus <- corpus(btw$text)
df.corpus <- dfm(all.corpus, removePunct = TRUE, removeSymbols = T)
```

```{r message=FALSE, warning=FALSE}
png("../figs/wordcloud.png")
textplot_wordcloud(df.corpus, max.word=300)
dev.off()
```
![Wordcloud 1](../figs/wordcloud.png)

@@

```{r eval=FALSE, include=FALSE}
wordclouds <- function(select_site) {
  corp <- btw %>% filter(site %in% select_site)
  corp <- corpus(corp$text_cleaned1)
  corp <- dfm(corp)

  textplot_wordcloud(corp, max.word=200)
}
```

```{r eval=FALSE, include=FALSE}
for (i in unique(btw$site)) {
  png(paste0("../figs/wordcloud_",i,".png"))
  wordclouds(i)
  dev.off()
}
```

@@

```{r echo = FALSE}
load("../output/models/STM 50 .Rda")
k <- stmOut$settings$dim$K
sagelabs <- sageLabels(stmOut, 20)
```

@@

```{r message=FALSE, warning=FALSE}
p <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
    geom_col(fill=col[3], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=9),
          axis.title = element_text(size=10))

@@

```{r fig.height=8, fig.width=12, message=FALSE, warning=FALSE}
p <- freq %>%
  mutate(topic =  as.numeric(gsub(":.*$","",topic))) %>% 
  ggplot(aes(reorder(topic_name,topic), freq)) +
  geom_col(fill = col[3]) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  theme(
    #axis.text.y = element_blank(),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="expected frequency")

@@

```{r eval=FALSE, include=FALSE}
btw.2 %>% filter(topic == 46) %>%
  filter(!grepl("Geißler", title)) %>%
  select(title, url, site) %>%
  htmlTable::htmlTable(align = "l")
```

@@

To identify which of these differences is significant, the conditional expectation of topic prevalence for given document characteristics can be estimated. More specifically, I estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation below).

$$
\theta_d=\alpha+\beta x_{ownership}+\epsilon
$$

@@

```{r}
coeff_tab <- coeff %>%
  filter(topic %in% keep) %>%
  select(topic_name,parameter,Estimate, `Std. Error`, `t value`, p)

print(xtable(coeff_tab[1:56,], type="latex", digits=3), 
      file="../writing/tables/coeff1.tex" )
print(xtable(coeff_tab[57:nrow(coeff_tab),], type="latex", digits=3), 
      file="../writing/tables/coeff2.tex" )
```

@@

```{r fig.height=4, fig.width=10}
p1 <- coeff %>% 
  filter(topic %in% keep) %>%
  filter(parameter != "(Intercept)") %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col(alpha = 0.8) +
  scale_fill_manual(values = col[c(5,3)]) +
  scale_x_discrete(position = "top") +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))
ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 9, height = 6,
dpi = 600)
```

@@

```{r eval=FALSE, fig.height=8, fig.width=4}
for (topic in keep) {

  png(filename = paste0("../figs/plotquote",topic,".png"), width = 300,
      height = 700)

  plotQuote(c(paste(sagelabs$covnames[1],":", 
                  paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[2],":",
                  paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[3],":", 
                  paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[4],":", 
                  paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[5],":", 
                  paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[6],":",
                  paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[7],":",
                  paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n"))),
          text.cex = 0.8, width = 40,
          main = paste(topics.df$topic_name[topics.df$topic==topic])
          )
  dev.off()
}
```

@@

@@

The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper. Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.

@@

##### By Month & Topic
```{r eval=FALSE, include=FALSE}
p <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  left_join(., tally_month, by = "yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w)

p1 <- ggplot(p, 
       aes(yearmonth, sentiment_w, 
           group = topic_name,
           label = obs)) +
  facet_wrap(~topic_name, nrow = 3, 
             labeller=labeller(topic_name = linebreak)) +
  geom_col(fill = col[3], alpha = 0.8) +
 geom_line(color = col[5], size = 0.6) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  labs(x="", y="Sentiment Score",
        title = "",
       subtitle = "") +
  scale_x_date(breaks = date_breaks("1 month"), 
               labels = date_format("%b-%y", tz ="CET")) +
  theme(strip.text = element_text(size=14),
    axis.text.y = element_text(size=10),
    axis.title.y = element_text(size=12),
        axis.text.x = element_text(size = 12, angle = 45))

ggsave(filename = "../figs/sentscore_monthly.png", plot = p1, 
       height = 10, width = 13)
```

@@

```{r eval=FALSE, include=FALSE}
p <- sentDF.values %>%
  group_by(site, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  left_join(., tally_site, by = "site") %>%
  mutate(w = obs/total_obs,
         sentiment_w = sentiment * w)

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment_w, 
           group = site,
           label = obs)) +
  geom_col(fill=col[3], alpha = 0.8) +
  #geom_line(color = col[2], size = 0.8) +
  #geom_text(size = 2) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="Sentiment Score",
       title = "") +
  theme(strip.text = element_text(size = 11),
    axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size=8, angle = 90),
        axis.title.x = element_text(size = 12))

@@

```{r eval=FALSE, fig.height=8, fig.width=10, include=FALSE}
sentDF.values %>%
mutate(topic_name = linebreak(topic_name)) %>%
  group_by(site, topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  left_join(., tally_site, by = "site") %>%
  mutate(w = obs/total_obs,
         sentiment_w = sentiment * w) %>%
  select(site, topic_name, sentiment_w) %>%
  spread(key=topic_name, value=sentiment_w) -> radar

p <- radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0) +
  labs(title = "") +
  guides(col = guide_legend(ncol = 7)) +
  theme(legend.position = "bottom",
        legend.text = element_text(size=14),
        legend.title = element_text(size=0),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

@@

```{r include=FALSE}
p <- polls %>%
  filter(yearmonth > as.Date("2017-01-01")) %>%
  filter(!party %in% c("Piraten", "Sonstige")) %>%
  ggplot(aes(Datum, value, 
             group = party,
             color = party)) +
  geom_line() +
  scale_color_manual(values =  c("deepskyblue", "gold", "limegreen", "deeppink", "red", "black")) +
  scale_x_date(breaks = date_breaks("1 month"), 
               labels=date_format("%b", tz="CET")) +
    geom_vline(xintercept = as.Date("2017-09-24"), 
             linetype = 2, color = col[3]) +
  labs(x="", y="", color="",
       title = "",
       caption = "source: infratest dimap") +
    guides(color = guide_legend(nrow = 1,
                                label.theme = element_text(size = 6,
                                                           angle=0))) +
  theme(axis.text = element_text(size=6),
        legend.position = "bottom")

@@

print(xtable(corr_tab, type="latex", digits=3,
                   caption = "Cross Correlation at lag 0"),
      file="../writing/tables/corr.tex" )
```

>>>>

```{r include=FALSE}
library(ggplot2)     # Static data visualization
library(dplyr)       # Data manipulation
library(stringr)     # String manipulation
library(lubridate)   # Date and time manipulation
library(purrr)       # Functional programming
library(tidyr)       # Reshaping
library(magrittr)    # Advanced piping
library(pushoverr)   # Pushover notifications
library(readr)       # Importing data
library(data.table)
library(stm)
#library(tm)
library(readxl)
library(Matrix)
library(psych)
library(xtable)
library(quanteda)

library(ggridges)
library(igraph)
library(corrplot)
#library(patchwork)
library(ggpmisc)
library(tidygraph)
library(RColorBrewer) 
library(ggrepel)
library(scales)      # Scales
library(wordcloud)

@@

theme_set(
  theme_bw(base_family = "Roboto", base_size = 10) +
    theme(
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 8),
      plot.caption = element_text(size = 6),
      panel.border = element_blank()
    )
)

#rm(list=ls())
col <- rcartocolor::carto_pal(12, "Bold")
source("func/functions.R")
```

@@

```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col[3], alpha = 0.8) +
  labs(x="", y="Number of articles") +
    coord_flip() +
  theme(
    axis.text.y = element_text(size = 12),
      legend.position   = "none"
    )

},
filename = "../figs/bar.png", device = "png", 
width = 6, height = 4,
        dpi = 600)
```

![plot1](../figs/bar.png)
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  group_by(date) %>%
  dplyr::summarise(obs = n()) %>%
  ggplot(aes(date, obs)) +
  geom_line(color=col[3]) +
  geom_vline(aes(xintercept=as.Date("2017-09-24")),
             linetype = 2, color=col[5]) +
  geom_vline(aes(xintercept=as.Date("2017-11-19")),
             linetype = 2, color=col[5]) +
  scale_color_manual(values = col) +
  labs(x="", y="Number of Articles",color="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%b\n%y", tz="CET")) +
  theme(
      legend.position   = "none",
      axis.title.x      = element_blank(),
      axis.text       = element_text(size = 10)
    )
},
filename = "../figs/timeline.png", device = "png",width = 6, height = 4,
dpi = 600
)

@@

print(xtable(output, type="latex", caption = "Summary statistics of text length",
             ref = "t_wordcount"), 
      file="../writing/tables/wordcount.tex" )

@@

ggsave(plot = {
  btw %>%
    ggplot(aes(as.numeric(text_length.cut), site)) +
    geom_density_ridges(scale = 4,
                        fill = col[3], alpha = .8,
                        color = "white") +
    labs(x = "Word count", y = "") +
    scale_x_continuous(expand = c(0,0), 
                       breaks = c(seq(0,2000,200)),
                       labels = c(seq(0,1800,200), ">2000")) +
    theme(axis.text = element_text(size = 12))

@@

### Unprocessed Text

```{r eval=FALSE, include=FALSE}
png("../figs/wordcloud.png", width = 350, height = 350)
wordcloud(btw$text, max.words = 100)
dev.off()
```
![Wordcloud](../figs/wordcloud.png)

@@

```{r eval=FALSE, include=FALSE}
wordclouds <- function(select_site) {
  tempdf <- btw %>% filter(site %in% select_site)

  wordcloud(tempdf$text_cleaned, max.word=50)
}
```

```{r eval=FALSE, include=FALSE}
for (i in unique(btw$site)) {
  png(paste0("../figs/wordcloud_",i,".png"), 
      width = 350, height = 350)
  wordclouds(i)
  dev.off()
}
```

@@

```{r echo = FALSE}
load("../output/models/STM 50 .Rda")
k <- stmOut$settings$dim$K
sagelabs <- sageLabels(stmOut, 15)
```

@@

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
p <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
    geom_col(fill=col[3], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=9),
          axis.title = element_text(size=10))

@@

```{r eval=FALSE, fig.height=8, fig.width=12, message=FALSE, warning=FALSE, include=FALSE}
p <- freq %>%
  mutate(topic =  as.numeric(gsub(":.*$","",topic))) %>% 
  ggplot(aes(reorder(topic_name,topic), freq)) +
  geom_col(fill = col[3]) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  theme(
    #axis.text.y = element_blank(),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="expected frequency")

@@

@@

To identify which of these differences is significant, the conditional expectation of topic prevalence for given document characteristics can be estimated. More specifically, I estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents.

@@

```{r eval=FALSE, include=FALSE}
coeff_tab <- coeff %>%
  filter(topic %in% keep) %>%
  select(topic_name,parameter,Estimate, `Std. Error`, `t value`, p)

print(xtable(coeff_tab[1:56,], type="latex", 
             digits=3), 
      include.rownames = F,
      file="../writing/tables/coeff1.tex" )
print(xtable(coeff_tab[57:nrow(coeff_tab),], 
             type="latex", 
             digits=3),
      include.rownames = F,
      file="../writing/tables/coeff2.tex" )

# add "\begin{adjustbox}{width=\textwidth,totalheight=\textheight,keepaspectratio}" and delete "\begin{table}" in latex document.
```

@@

```{r fig.height=4, fig.width=10}
p1 <- coeff %>% 
  filter(topic %in% keep) %>%
  filter(parameter != "(Intercept)") %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col(alpha = 0.8) +
  scale_fill_manual(values = col[c(5,3)]) +
  scale_x_discrete(position = "top") +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=11),
        axis.text.x = element_text(angle=90))
ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 9, height = 6,
dpi = 600)
```

@@

```{r eval=FALSE, include=FALSE}
for (topic in keep) {

  png(filename = paste0("../figs/plotquote",topic,".png"), width =500,
      height = 700)

  plotQuote(c(paste(sagelabs$covnames[1],":", 
                  paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[2],":",
                  paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[3],":", 
                  paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[4],":", 
                  paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[5],":", 
                  paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[6],":",
                  paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[7],":",
                  paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n"))),
          text.cex = 1.3, width = 50,
          main = paste0("Topic: ", topics.df$topic[topics.df$topic==topic])
          )
  dev.off()
}
```

@@

```{r}
samp <- sent %>% dplyr::sample_n(10)

print(xtable(samp, type="latex", label = "t_sentdict",
             caption = "Sentiment Dictionary (Sample)"), 
      file="../writing/tables/sent_dict.tex" )

knitr::kable(samp)
```

@@

The following table shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper. Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.

@@

##### By Month & Topic
```{r eval=FALSE, include=FALSE}
p <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  left_join(., tally_month, by = "yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w) %>%
  dplyr::arrange(topic) %>%
  select(yearmonth, topic_name, obs, sentiment_w) %>%
  ungroup()
```

```{r eval=FALSE, include=FALSE}
# save to latex files
num <- nrow(p)/2
num1 <- num+1

p.tab <- p %>%
  transmute(date = as.character(yearmonth),
             topic = topic_name,
             `Number of Obs.` = obs,
             `sentiment value * 1000` = sentiment_w*1000
             )

print(xtable(p.tab[1:num,], 
             type="latex"
             ), include.rownames = F,
      file="../writing/tables/sentscore_monthly1.tex" )

print(xtable(p.tab[num1:nrow(p.tab),], 
             type="latex"
             ), include.rownames = F,
      file="../writing/tables/sentscore_monthly2.tex" )

# add "\begin{adjustbox}{width=\textwidth}" and delete "\begin{table}" in latex document. 
```

```{r}
p %>%
  knitr::kable()
```

$$
\text{normalized_w} = \frac{w - \min{(W)}}{\max{(W)}-\min{(W)}}
$$

```{r eval=FALSE, include=FALSE}
p1 <- ggplot(p, 
       aes(yearmonth, normalize_data(sentiment_w), 
           group = topic_name,
           label = obs)) +
  facet_wrap(~topic_name, nrow = 5) +
  geom_col(fill = col[3], alpha = 0.8) +
  geom_line(color = col[5], size = 0.6) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  labs(x="", y="Sentiment Score",
        title = "",
       subtitle = "") +
  scale_x_date(breaks = date_breaks("1 month"), 
               labels = date_format("%b-%y", tz ="CET")) +
  theme(strip.text = element_text(size=14),
    axis.text.y = element_text(size=10),
    axis.title.y = element_text(size=12),
        axis.text.x = element_text(size = 12, angle = 90))

ggsave(filename = "../figs/sentscore_monthly.png", plot = p1,
       height = 12, width = 12)
```

@@

```{r eval=FALSE, include=FALSE}
p <- sentDF.values %>%
  group_by(site, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  left_join(., tally_site, by = "site") %>%
  mutate(w = obs/total_obs,
         sentiment_w = sentiment * w) %>%
  select(site, topic_name, obs, topic, sentiment_w) %>%
  ungroup()
```

```{r eval=FALSE, include=FALSE}
# save to latex files
num <- nrow(p)/2
num1 <- num+1

p.tab <- p %>%
  transmute(`News website` = site,
             topic = topic_name,
             `Number of Obs.` = obs,
             `sentiment value * 1000` = sentiment_w*1000
             )

print(xtable(p.tab[1:num,], 
             type="latex"), 
      include.rownames = F,
      file="../writing/tables/sentscore_site1.tex" )

print(xtable(p.tab[num1:nrow(p.tab),],
             type="latex"
             ), 
      include.rownames = F,
      file="../writing/tables/sentscore_site2.tex" )

# add "\begin{adjustbox}{width=\textwidth}" and delete "\begin{table}" in latex
```

```{r}
p %>%
  knitr::kable()
```

```{r eval=FALSE, include=FALSE}
p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           normalize_data(sentiment_w), 
           group = site,
           label = obs)) +
  geom_col(fill=col[3], alpha = 0.8) +
  #geom_line(color = col[2], size = 0.8) +
  #geom_text(size = 2) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="Sentiment Score",
       title = "") +
  theme(strip.text = element_text(size = 11),
    axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size=10, angle = 90),
        axis.title.x = element_text(size = 14))

@@

```{r eval=FALSE, fig.height=8, fig.width=10, include=FALSE}
sentDF.values %>%
mutate(topic_name = linebreak(topic_name)) %>%
  group_by(site, topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  left_join(., tally_site, by = "site") %>%
  mutate(w = obs/total_obs,
         sentiment_w = sentiment * w) %>%
  #mutate(sentiment_w = normalize_data(sentiment_w)) %>%
  select(site, topic_name, sentiment_w) %>%
  spread(key=topic_name, value=sentiment_w) -> radar
```

```{r eval=FALSE, include=FALSE}
p <- ggRadar(radar, aes(color=site),
          rescale = F,
          alpha = 0) +
  labs(title = "") +
  guides(col = guide_legend(ncol = 7)) +
  theme(legend.position = "bottom",
        legend.text = element_text(size=14),
        legend.title = element_text(size=0),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

@@

```{r include=FALSE}
p <- polls %>%
  filter(yearmonth > as.Date("2017-01-01")) %>%
  filter(!party %in% c("Piraten", "Sonstige")) %>%
  ggplot(aes(Datum, value, 
             group = party,
             color = party)) +
  geom_line() +
  scale_color_manual(values =  c("deepskyblue", "gold", "limegreen", "deeppink", "red", "black")) +
  scale_x_date(breaks = date_breaks("1 month"), 
               labels=date_format("%b\n%y", tz="CET")) +
    geom_vline(xintercept = as.Date("2017-09-24"), 
             linetype = 2, color = col[3]) +
  labs(x="", y="", color="",
       title = "",
       caption = "source: infratest dimap") +
    guides(color = guide_legend(nrow = 1,
                                label.theme = element_text(size = 10,
                                                           angle=0))) +
  theme(axis.text = element_text(size=10),
        legend.position = "bottom")

@@

print(xtable(corr_tab, type="latex", digits=3,
             label = "t_ccf",
                   caption = "Cross Correlation at lag 0"),
      file="../writing/tables/corr.tex" )
```
